Constraining the Interiors of Asteroids Through Close Encounters

### 2022-06-29 paper/main.tex
New threshold plots and lumpy double model

The lumpy model also yields distributions which are consistent with the extracted moments and consistent with uniform (the $\chi^2_r$ values are large due to numerical error and correspond to deviations in $K_{2m}$ only on the order of \jtd{number}). These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of \jtd{number}) due to its few degrees of freedom. With only one lump, the location of the known center of mass requires that the lump lie at the centroid of the asteroid center with mass close to zero and unconstrained radius. Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more apt to be contained inside a lump. In order for the lumpy model to converge given the unconstrained lump radius, we use the mass-weighted $\mu_i a_i \rightarrow 0$ as a model parameter rather than the lump length $a_i$.

>>>>

The lumpy model also yields distributions which are consistent with the extracted moments and consistent with uniform. These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of \jtd{number}) due to its few degrees of freedom. With only one lump, the location of the known center of mass requires that the lump lie at the centroid of the asteroid center with mass close to zero and unconstrained radius. Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more apt to be contained inside a lump. In order for the lumpy model to converge given the unconstrained lump radius, we use the mass-weighted $\mu_i a_i \rightarrow 0$ as a model parameter rather than the lump length $a_i$.
